\textbf{\sc Towards Deliberative Control in Marine Robotics}

### 2012-02-23 trunk/arch.tex
Typos in arch.tex

It is important to note that in T-REX architecture the only critical
task of a reactor is to sucessfully identify its state through
synchronization as the execution frontier advances. Indeed, a reactor
that fails to integrate its {\em external} state updates and/or
identify its {\em internal} state at any tick express that it is not
able anymore to explain the state of the world. In the agent point of
view that means that any state information from this reactor is not to
be trucsted anymore and will result on this reactor exclusion from the
execution cycle. As the agent destroy the  faulty reactor is
destraoyed the agent produced on all of its former {\em internal}
timelines the special observation \texttt{Failed} to all the reactors
which did declare these state variables as {\em external} informing
them through this that this sepcific state varaiable is currently
unavailable. On the other hand all goals exchanged between reactors
are considered as rejectable by the reactor that manages them. As a
result the falure to find a plwn for these goals, while to be avoided,
is not considered as a critical failure of the reactor and will only
result on these goals being ignored until new goals are received.

Take for example our AUV agent from Fig. \ref{fig:agent},
and assume that the \texttt{Sampling} reactor failed to synchronize;
in  such case this reactor is destroyed and both
\texttt{Sampling\_policy} and \texttt{Relevant\_data} state variables
produced the \texttt{Failed} observation. Therefore, the
\texttt{Survey controller} will received this observation on its {\em
  external} \texttt{Sampling\_policy} which indicates that this state
varaiable is not managed anymore. At this point depending on this
reactor implementationm we have two possible outcomes:
\begin{enumerate}
\item \texttt{Survey  controller} model allows him to integrate this
  \texttt{Failed} observation. For example it can integarte that from
  now there's now way to take water samples. It is still able to
  navigate as \texttt{Pilot} is still available which allow him to
  continue this aspect of its current plan.
\item \texttt{Survey controller} models is not able to handle this
  unexpected failure resulting in turn on its failure to
  synchronize. This result on this reactor being also destroyed and
  the \texttt{Failed} observation is produced on the \texttt{survey}
  timeline.
\end{enumerate}
Even on the worst case scenario of the later case, we
note that a reactor failure only propagates up in the reactor graph. 
In our example, even if all the reactors that depends on
\texttt{Sampling} are entrained by its failure, we still keep the
three reactors \texttt{Vehicle}, \texttt{Pilot} and \texttt{Ship
  operation} allowing to  maintain the vehicle navigation control
(\texttt{Pilot}) along with high level safety operation 
(\texttt{Ship operation}). It illustrates how \rx can handle graceful
system degradation despite the failure of one or more reactors. It
also emphasize that it is critical to ensure that the low level
reactors are properly designed in order to be as robust as 
possible.

@@

While the two processes are separate, they share the same plan
internal to a reactor; consequently at every synchronization cycle the
planning process is informed of the new world state and its impact on
the plan. Conversely, when synchronization occurs after deliberation
stops, its starting point is the last partial plan resulting from
deliberation. This gives an initial frame to the problem that helps to
target the synchronization problem by ensuring that the new {\em
  external} state updates are compatible with this plan. If so,
synchronization propagates these events in the plan and can use it as
an aid in resolving its {\em current state flaw}. It does so by using
the plan information on the exepected {\em internal} state evolution
near the execution frontier.

@@

In the real world the fact that the robot is \texttt{Going} to a
certain location does not necessarly imply that it will succeed in
ending up there. Due to an exogenous event, for example, the road to
the \texttt{SuperMarket} could be closed, which could result in an
alternate observation that the robot is \texttt{At(7th st. \& Main)}
contradicting the existing plan. Further, it is important to
understand the temporal direction of the \emph{causal link} that is
triggering the inconsistency. At the time the robot observes the
contradiction of the \texttt{At} predicate, the rule that generated
this conflict is connected to past observations \texttt{Going} and
\texttt{Go}. These cannot be retracted easily without a potential
impact to the plan implying in terms of a cost in back-propagation.

@@

This choice is directed not only by heuristic choices made in the
solver but also enforced by the heuristic order of the decision point
resolution choices for the {\em current state flaw} shown in
Proposition \ref{prop:csf:resolve}. As noted, the first two choices
are biased towards a conservative view with respect to the existing
plan. The heuristics first attempt to extend the previous observation
for this {\em internal} timeline to avoid early commitment. If this
fails \rx attempts to start the next existing token in the plan to
advance plan execution. Both choices attempt to resolve state with the
least amount of plan perturbation by constraining further the start
and end time of existing tokens generated by previous deliberations
steps. By doing so, in a nominal situation, synchronization remains
limited to restrict time points in the plan and propagates their
impact. Most of the computational effort of creating new tokens in the
plan and scheduling them onto timelines are managed during
deliberation steps. Consequently, most of the time synchronization is
limited to very few nodes in the \eu search space often requiring no
backtracking. Fig. \ref{fig:shop:exec} shows how the existing plan can
support the synchronization process. The observation \texttt{Going}
occuring at $\tau'$ is fully compatible with the token already present
in our plan. By updating the plan and progating equality constraints,
the resolution of the {\em current state flaw} for the {\em Agent}
timeline becomes obvious as a solution, as the token \texttt{Go} from
the plan presents itself.

@@

% In that sense, and thanks to the carefull choice on our
% synchronization heurisitic we see that the plan produced during \rx
% deliberation steps helps sthe synchronization process to be more
% efficient.

@@

% As long as one can ensure that synchronization of all
% reactors and deliberation steps can be done within a time that is
% resonably small in comparison to the agent tick duration.

>>>>

It is important to note that, in T-REX architecture, the only critical
task of a reactor is to successfully identify its state through
synchronization as the execution frontier advances. Indeed, a reactor
that fails to integrate its {\em external} state updates and/or
identify its {\em internal} state at any tick express that it is not
able anymore to explain the state of the world. In the agent point of
view that means that any state information from this reactor is not to
be trusted anymore and results on this reactor exclusion from the
execution cycle and consequent destruction. As the agent destroy 
the  faulty reactor is destroyed the agent produced on all of 
its former {\em internal} timelines the special observation 
\texttt{Failed} to all the reactors which did declare these state 
variables as {\em external} informing
them through this that this specific state variable is currently
unavailable. On the other hand all goals exchanged between reactors
are considered as rejectable by the reactor that manages them. As a
result the failure to find a plan for these goals, while to be avoided,
is not considered as a critical failure of the reactor and will only
result on these goals being ignored until new goals are received.

Take for example our AUV agent from Fig. \ref{fig:agent},
and assume that the \texttt{Sampling} reactor failed to synchronize;
in  such case this reactor is destroyed and both
\texttt{Sampling\_policy} and \texttt{Relevant\_data} state variables
produced the \texttt{Failed} observation. Therefore, the
\texttt{Survey controller} will received this observation on its {\em
  external} \texttt{Sampling\_policy} which indicates that this state
variable is not managed anymore. At this point depending on this
reactor implementation we have two possible outcomes:
\begin{enumerate}
\item \texttt{Survey  controller} model allows him to integrate this
  \texttt{Failed} observation. For example it can integrate that from
  now there's now way to take water samples. It is still able to
  navigate as \texttt{Pilot} is still available which allow him to
  continue this aspect of its current plan.
\item \texttt{Survey controller} models is not able to handle this
  unexpected failure resulting in turn on its failure to
  synchronize. This result on this reactor being also destroyed and
  the \texttt{Failed} observation is produced on the \texttt{survey}
  timeline.
\end{enumerate}
Even on the worst case scenario presented on this second case, we
note that a reactor failure only propagates up in the reactor graph. 
In our example, even if all the reactors that depends on
\texttt{Sampling} are entrained by its failure, we still keep the
three reactors \texttt{Vehicle}, \texttt{Pilot} and \texttt{Ship
  operation} allowing to  maintain the vehicle navigation control
(\texttt{Pilot}) along with high level safety operation 
(\texttt{Ship operation}). It illustrates how \rx can handle graceful
system degradation despite the failure of one or more reactors. It
also emphasize that it is critical to ensure that the low level
reactors are properly designed in order to be as robust as 
possible.

@@

While the two processes are separate, they share the same plan
internal to a reactor; consequently at every synchronization cycle the
planning process is informed of the new world state and its impact on
the plan. Conversely, when synchronization occurs after deliberation
stops, its starting point is the last partial plan resulting from
deliberation. This gives an initial frame to the problem that helps to
target the synchronization problem by ensuring that the new {\em
  external} state updates are compatible with this plan. If so,
synchronization propagates these events in the plan and can use it as
an aid in resolving its {\em current state flaw}. It does so by using
the plan information on the expected {\em internal} state evolution
near the execution frontier.

@@

In the real world the fact that the robot is \texttt{Going} to a
certain location does not necessarily imply that it will succeed in
ending up there. Due to an exogenous event, for example, the road to
the \texttt{SuperMarket} could be closed, which could result in an
alternate observation that the robot is \texttt{At(7th st. \& Main)}
contradicting the existing plan. Further, it is important to
understand the temporal direction of the \emph{causal link} that is
triggering the inconsistency. At the time the robot observes the
contradiction of the \texttt{At} predicate, the rule that generated
this conflict is connected to past observations \texttt{Going} and
\texttt{Go}. These cannot be retracted easily without a potential
impact to the plan implying in terms of a cost in back-propagation.

@@

This choice is directed not only by heuristic choices made in the
solver but also enforced by the heuristic order of the decision point
resolution choices for the {\em current state flaw} shown in
Proposition \ref{prop:csf:resolve}. As noted, the first two choices
are biased towards a conservative view with respect to the existing
plan. The heuristics first attempt to extend the previous observation
for this {\em internal} timeline to avoid early commitment. If this
fails \rx attempts to start the next existing token in the plan to
advance plan execution. Both choices attempt to resolve state with the
least amount of plan perturbation by constraining further the start
and end time of existing tokens generated by previous deliberations
steps. By doing so, in a nominal situation, synchronization remains
limited to restrict time points in the plan and propagates their
impact. Most of the computational effort of creating new tokens in the
plan and scheduling them onto timelines are managed during
deliberation steps. Consequently, most of the time synchronization is
limited to very few nodes in the \eu search space often requiring no
backtracking. Fig. \ref{fig:shop:exec} shows how the existing plan can
support the synchronization process. The observation \texttt{Going}
occurring at $\tau'$ is fully compatible with the token already present
in our plan. By updating the plan and propagating equality constraints,
the resolution of the {\em current state flaw} for the {\em Agent}
timeline becomes obvious as a solution, as the token \texttt{Go} from
the plan presents itself.

@@

% In that sense, and thanks to the careful choice on our
% synchronization heuristic we see that the plan produced during \rx
% deliberation steps helps the synchronization process to be more
% efficient.

@@

% As long as one can ensure that synchronization of all
% reactors and deliberation steps can be done within a time that is
% reasonably small in comparison to the agent tick duration.
